Final Project Data 205

### 2021-12-07 Draft Final Project1.Rmd
Add files via upload

## 
```{r}
tuition$tuition$name[grepl('State University of New York', tuition$name)] <- 
```

@@

```{r}
,url_exception_june_2020,url_exception_july_2020,url_exception_september_2019,url_exception_august_2019,url_exception_july_2019,url_exception_march_2019,url_exception_february_2019,url_exception_january_2019,url_exception_december_2018,url_exception_september_2018,url_exception_august_2018,url_exception_july_2018,url_exception_june_2018,url_exception_may_2018,url_exception_april_2018,url_exception_december_2017,url_exception_november_2017,url_exception_june_2017,url_exception_april_2017,url_exception_march_2017,url_exception_january_2017
```

## Clean the WMATA data with NA's
```{r}

# Create Groupby Year & State (test)
```{r}
df_state<- df_wmata %>%
group_by(year) %>%
select(DC,MD,VA)
summarize(sum = sum(state), count = n()) %>%
arrange(year, state)

df_state
```

>>>>

## Rename variables (State)
```{r}
WMATA$state[grepl('PG',WMATA$state)]<- 'MD'
WMATA$state[grepl('MC',WMATA$state)]<- 'MD'
WMATA$state[grepl('RL',WMATA$state)]<- 'VA'
WMATA$state[grepl('EX',WMATA$state)]<- 'VA'
```

## Create a New Column and Add Months and years to WMATA DataSet 
```{r}
mutate(date=as.Date(date,format="%Y"))
```

## Groupby Time Series( Define Time (Morning, DayTime, Night)

```{r}
#Create a time series 
```

## Plot 1
```{r}
p1<-WMATA  %>%
  filter(state %in% c("DC","MD","VA")) %>%
  ggplot(aes(x=state, fill= state))+
  geom_bar()+
  labs(title="Total of Crimes by State/District",x="State/District", y="Total")+
  scale_fill_brewer(palette = "Dark2") + theme_minimal()
p1 + theme_minimal()
```

## Plot Types of Crime
```{r}
p2<-WMATA  %>%
  filter(type %in% c("ARREST","REPORT","SUMMONS/CITATION")) %>%
  ggplot(aes(x=type, fill= type))+
  geom_bar()+
  labs(title="Classification of Type of Crime/ Reporting",x="Type", y="Total")+
  scale_fill_brewer(palette = "Blues") + theme_minimal()
p2 + theme_minimal()
```

@@
